The Parareal Algorithm for Parallel Solution of ODEs

### 2014-12-09 poster/main.tex
updated algo to hopefully use a bit less time; updated poster

Input: Temporal discretization $t^n = t_0 + n \Delta t, \, n = 1,2,\ldots,N$
Input: Coarse scheme $g_{\Delta t}$
Input: Finer scheme $g_{\textnormal{fine}}$
Compute $u_1^{n+1} = g_{\Delta t}(t^n, u^n)$
Compute the corrections $\delta g^n(u_1^n) = g_{\textnormal{fine}}(t^n,
u^n) - g_{\Delta t}(t^n, u^n)$ in parallel
Add the prediction and correction terms as $u_2^{n+1} = g_{\Delta
t}(t^n, u_2^n) + \delta g^n(u_1^n)$
Repeat steps 2 and 3, incrementing the iteration label and using $u_{k+1}^0
= u^0$ as the initial condition
\end{block}

>>>>

\begin{itemize}
    \item \textbf{Input}: Temporal discretization $t_n = t_0 + n \Delta t, \, n =
        1,2,\ldots,N$
    \item \textbf{Input}: Coarse scheme $g_{\Delta t}$
    \item \textbf{Input}: Finer scheme $g_{\textnormal{fine}}$
\end{itemize}

\begin{enumerate}
    \item Compute $u^1_{n+1} = g_{\Delta t}(t_n, u^1_n)$
    \item Compute the corrections $\delta g_n(u_1_n) =
        g_{\textnormal{fine}}(t_n, u^1_n) - g_{\Delta t}(t_n, u^1_n)$ in parallel
    \item Add the prediction and correction terms as $u^2_{n+1} = g_{\Delta
        t}(t_n, u^2_n) + \delta g_n(u^1_n)$
    \item Repeat steps 2 and 3, incrementing the iteration label and using
        $u^{k+1}_0 = u^1_0$ as the initial condition
\end{enumerate}
\end{block}
